CF Registry Analysis

### 2023-05-22 Christine Chan/CF Registry/cf_registry_analysis.qmd
calculate percentiles from raw values

```{r}
#| include: false
library(knitr)
library(tidyverse)
library(forestmodel)
```

@@

Any participants with T1D or T2D were excluded from these analyses.

@@

log_reg = function(year = 2005){

@@

           A_bmivalue,A_bmipercentile,A_height,A_heightpercentile,
           NumPulmExacerbation,A_feeding2,A_pseudomonasaeruginosa,

@@

@@

                       labels = c("1-3","4-5","Oth",NA))

@@

  df$A_feeding2 = factor(df$A_feeding2,levels = 0:1,labels = c("No","Yes"))
  df$A_IsOnEnzymes = factor(df$A_IsOnEnzymes,levels = 0:1,labels = c("No","Yes"))
  df$A_FEV1_pct_predicted = cut(df$A_FEV1_pct_predicted,breaks = c(0,40,80,100,Inf),right = F)
  df$A_corticosteroids1 = factor(df$A_corticosteroids1,levels = 0:1,labels = c("No","Yes"))
  df$A_fungalyeast1 = factor(df$A_fungalyeast1,levels = 0:1,labels = c("No","Yes"))
  df$A_pulmonarycomplications1 = factor(df$A_pulmonarycomplications1,levels = 0:1,labels = c("No","Yes"))
  df$A_mycocultureresults1 = factor(df$A_mycocultureresults1,levels = 0:1,labels = c("No","Yes"))
  df$A_Vx770 = factor(df$A_Vx770,levels = 0:1,labels = c("No","Yes"))
  df$A_VX809comb = factor(df$A_VX809comb,levels = 0:1,labels = c("No","Yes"))
  df = df[,-which(colSums(is.na(df))==nrow(df))]

@@

@@

                                "A_bmipercentile","A_height","A_heightpercentile"))]

@@

  adult_mod = update(base_mod,.~.+A_bmivalue+A_height)
  peds_mod = update(base_mod,.~.+A_bmipercentile+A_heightpercentile)

@@

  adult_mod1 = glm(adult_mod,data = df,family = "binomial")
  peds_mod1 = glm(peds_mod,data = df,family = "binomial")

@@

  cat("### Base Models")

@@

  cat("#### Adult")
  print(forest_model(adult_mod1))
  cat("#### Peds")
  print(forest_model(peds_mod1))

@@

    adult_mod2 = glm(update(adult_mod,.~.+A_pseudomonasaeruginosa),data = df,family = "binomial")
    peds_mod2 = glm(update(peds_mod,.~.+A_pseudomonasaeruginosa),data = df,family = "binomial")

@@

    cat("#### Adult")
    print(forest_model(adult_mod2))
    cat("#### Peds")
    print(forest_model(peds_mod2))

@@

    adult_mod3 = glm(update(adult_mod,.~.+A_fungalyeast1),data = df,family = "binomial")
    peds_mod3 = glm(update(peds_mod,.~.+A_fungalyeast1),data = df,family = "binomial")

@@

    cat("#### Adult")
    print(forest_model(adult_mod3))
    cat("#### Peds")
    print(forest_model(peds_mod3))

@@

    adult_mod4 = glm(update(adult_mod,.~.+A_pulmonarycomplications1),data = df,family = "binomial")
    peds_mod4 = glm(update(peds_mod,.~.+A_pulmonarycomplications1),data = df,family = "binomial")

@@

    cat("#### Adult")
    print(forest_model(adult_mod4))
    cat("#### Peds")
    print(forest_model(peds_mod4))

@@

    adult_mod5 = glm(update(adult_mod,.~.+A_mycocultureresults1),data = df,family = "binomial")
    peds_mod5 = glm(update(peds_mod,.~.+A_mycocultureresults1),data = df,family = "binomial")

@@

    cat("#### Adult")
    print(forest_model(adult_mod5))
    cat("#### Peds")
    print(forest_model(peds_mod5))

@@

## 2005

```{r results='asis',fig.height=10,fig.width=10}
log_reg(2005)
```

>>>>

```{r}
#| include: false
library(knitr)
library(tidyverse)
library(forestmodel)
library(childsds)
```

@@

Any participants with T1D or T2D were excluded from these analyses. Variables that were entirely missing in a given year (e.g., `A_Vx770` and `A_VX809comb` in 2005) were excluded from those models.

@@

log_reg = function(year){

@@

           A_bmivalue,A_bmipercentile,A_height,A_weight,A_heightpercentile,
           NumPulmExacerbation,A_pseudomonasaeruginosa,

@@

  # Calculate percentiles
  df$bmi = df$A_weight / ((df$A_height/100)^2)
  df$age_perc = ifelse(df$Age_YrEnd < 20,df$Age_YrEnd,20)
  df$height_perc = sds(df$A_height,age = df$age_perc,
                    sex = df$Gender,male = "M",female = "F",
                    item = "height2_20",ref = cdc.ref,type = "perc")*100
  df$bmi_perc = sds(df$bmi,age = df$age_perc,
                    sex = df$Gender,male = "M",female = "F",
                    item = "bmi",ref = cdc.ref,type = "perc")*100

@@

                       labels = c("1-3","4-5","Oth","Unknown"))

@@

  df$A_FEV1_pct_predicted = cut(df$A_FEV1_pct_predicted,
                                breaks = c(0,40,80,100,Inf),right = F)
  df$A_FEV1_pct_predicted = relevel(df$A_FEV1_pct_predicted,ref = "[100,Inf)")
  df$height_perc = cut(df$height_perc,breaks = c(0,10,25,50,Inf))
  df$height_perc = relevel(df$height_perc,ref = "(50,Inf]")
  df$bmi_perc = cut(df$bmi_perc,breaks = c(0,10,50,85,Inf))
  df$bmi_perc = relevel(df$bmi_perc,ref = "(50,85]")
  df$age_group = cut(df$Age_YrEnd,breaks = c(0,10,18,30,Inf))
  df$age_group = relevel(df$age_group,ref = "(10,18]")

@@

  # Yes/No variables
  yn_vars = c("A_IsOnEnzymes","A_corticosteroids1",
              "A_Vx770","A_VX809comb",bugs)
  df[,yn_vars] = lapply(df[,yn_vars],factor,levels = 0:1,labels = c("No","Yes"))
  empty = which(colSums(is.na(df))==nrow(df))
  if(length(empty)>0){
    df = df[,-empty]

@@

                                "A_bmipercentile","A_height","A_heightpercentile",
                                "Age_YrEnd","A_weight","bmi", "age_perc"))]

@@

@@

  mod1 = glm(base_mod,data = df,family = "binomial")

@@

  cat("### Base Model")

@@

  print(forest_model(mod1))

@@

    mod2 = glm(update(base_mod,.~.+A_pseudomonasaeruginosa),data = df,family = "binomial")

@@

    print(forest_model(mod2))

@@

    mod3 = glm(update(base_mod,.~.+A_fungalyeast1),data = df,family = "binomial")

@@

    print(forest_model(mod3))

@@

    mod4 = glm(update(base_mod,.~.+A_pulmonarycomplications1),data = df,family = "binomial")

@@

    print(forest_model(mod4))

@@

    mod5 = glm(update(base_mod,.~.+A_mycocultureresults1),data = df,family = "binomial")

@@

    print(forest_model(mod5))

@@

## 2006

```{r results='asis',fig.height=10,fig.width=10}
log_reg(2006)
```

## 2013

```{r results='asis',fig.height=10,fig.width=10}
log_reg(2013)
```

## 2018

```{r results='asis',fig.height=10,fig.width=10}
log_reg(2018)
```
